Cartogram Mapping and its Application to Cancer Data Visualization

### 2019-09-30 review_article.Rmd
abstract

\section*{Abstract}
Choropleth maps are a traditional form of presenting spatial data.
They are widely used in cancer atlases, leveraging the familiar geographical regions to communicate cancer statistics around the world. The presentation of this data has improved with the developments in the statistics used to measure the impact of cancer on a population. Web atlases have utilized developments in interaction and animation techonolgies to empower individual users to explore cancer statistics for their own purposes. There has also been progress and contributions to alternative displays that present spatial data with varying levels of focus on the spatial distribution of a statistic. This work highlights the impact of the varying sizes of areas created by the administrative boundaries that define communities and affects the way that spatial impact of cancer on Australian communities is understood.
These displays are not often utilized in cancer atlases, this provides an opportunity to improve the communication of cancer statistics. Including alternative visualizations will provide users a new perspective on the spatial distribution of cancer statistics.

>>>>

\section*{Abstract}
Choropleth maps are widely used in cancer atlases, and traditionally communicate cancer statistics over geographic domains. The type of statistic displayed varies immensely, and effective choices can assist in the understanding of impact of cancer on a population. Atlases have moved from print media to web format, and the availability of graphical user interfaces, and user interaction and animation, greatly enhance the ability to communicate more information and positively engage readers. More use of alternatives to choropleth maps, such as cartograms, could be employed in online atlases, to better representation of spatial distributions, and show statistics on small areas. This is especially true for the geography of Australia, where the population is concentrated is small areas along the coastlines.
